\documentclass[a4paper,10pt]{article}
\usepackage{cv,booktabs,fontawesome5}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{hyperref}

% Change color to blue
\def\headcolor{\color[rgb]{0,0.3,0.5}}

% Space before section headings
\titlespacing{\section}{0pt}{2ex}{1ex}

\name{Rudolf Schlechter}

\info{\faIcon{map-marker-alt} & 4/589 Barbadoes street, \\
                          &  Christchurch 8013, New Zealand\\
      \faIcon{phone}      & +64 27 525 3637\\
      \faIcon{envelope}   & roschlec@gmail.com\\
      \faIcon{twitter}    & @rschlec\\
      \faIcon{github}     & \href{http://www.github.com/roschlec}{github.com/roschlec}\\
      \faIcon{orcid}      & \href{https://orcid.org/0000-0002-5717-2917}{0000-0002-5717-2917}\\
      \faIcon{graduation-cap} & \href{https://scholar.google.com/citations{?}user=D3zhLzEAAAAJ{&}hl=en}{Google Scholar h-index = 9.0}\\
      \faIcon{globe-americas} & Chilean and German}

\bibliography{rjhpubs}

\DeclareSourcemap{
  \maps[datatype=bibtex, overwrite]{
    \map{
      \step[fieldset=month, null]
    }
  }
}

% Use useprefix because of Ashton de Silva
\ExecuteBibliographyOptions{useprefix=true}

\usepackage[sfdefault,lf,t]{carlito}
\renewcommand{\bibfont}{\normalfont\fontsize{10}{12.4}\sffamily}
\usepackage{inconsolata}

\makebibcategory{selected}{Selected refereed research papers}

\addtocategory{books}{
  MWH3,
  expsmooth08,
  fpp2,
}

\addtocategory{selected}{
  YW93,
  HDRF95,
  HDR96,
  HBG96,
  HF96,
  GHH97,
  HKSG02,
  HHF04,
  HKOS05,
  HK06,
  HU07,
  HB08,
  HK08,
  HS09,
  HS10,
  HF10,
  hierarchical,
  DHS11,
  HBY13,
  gefcom,
  m3pca,
  %hfts,
  mint,
  boostingar,
  probhts,
  bagginguncertainty,
  forecastingsofa,
  oddstream,
  }



\begin{document}
\maketitle

\section{Education and Qualifications}

~\begin{tabular}{llll}
2017- & Ph.D. \textit{Microbiology} & University of Canterbury & New Zealand\\
& \multicolumn{3}{l}{\small\textcolor{black!70}{Thesis title: ``Diving factors of bacterial interactions and spatial patterns in the phyllosphere''}}\\
& \multicolumn{3}{l}{\small\textcolor{black!70}{Senior Supervisor: Mitja Remus-Emsermann, PhD}}\\
& \multicolumn{3}{l}{\small\textcolor{black!70}{Associate Supervisor: Prof. Emerita Paula Jameson, Matthew Stott, PhD}}\\
2013-2014 & Licenciate \textit{Biochemistry} (M.Sc. equivalent) & Pontificia Universidad de Chile & Chile\\
& \multicolumn{3}{l}{\small\textcolor{black!70}{Thesis title: ``Characterisation of the immune response conferred by the \textit{loci} RUN1 and REN1 in \textit{Vitis vinifera}}}\\
& \multicolumn{3}{l}{\small\textcolor{black!70}{against \textit{Erysiphe necator}''}}\\
& \multicolumn{3}{l}{\small\textcolor{black!70}{Senior Supervisor: Patricio Arce-Johnson, PhD}}\\
2009-2013 & B.Sc. \textit{Biochemistry} & Pontificia Universidad de Chile & Chile
\end{tabular}

\section{Honours and awards}

~\begin{tabular}{ll}
%2017 & Visiting Expert Professor, Chinese Academy of Sciences, Beijing, China.\\
2016 & KNAW Visiting Professor, TU/Eindhoven, Netherlands.\\
2010 & Dean's Award for excellence in innovation and external collaboration, Monash University.\\
2010 & HP Innovation Research Award.\\
%2009--2010 & Entry in \emph{Great minds of the 21st century}, 1st--4th editions.\\
2008 & Dean's award for excellence in research, Monash University.\\
2008 & Vice-Chancellor's award for postgraduate supervisor of the year, Monash University.\\
2007 & Knibbs Lecturer, Statistical Society of Australia (ACT branch).\\
2007 & Moran Medal for Statistical Science, Australian Academy of Science.\\
2006 & Belz Lecturer, Statistical Society of Australia (Victorian branch).
\end{tabular}

\section{Research}

\begin{itemize}\parskip=0cm
\item Since 1991 I have authored 195 papers, chapters or books on statistical topics. A list of selected publications appears on the following page.
\item  My current research involves the analysis of large collections of time series, and includes visualization, forecasting, reconciliation and modelling. Applications include electricity demand and smart-meter data, security sensors, manufacturing data and retail sales.
\item I currently supervise seven PhD students and three post-doctoral research fellows. I have previously supervised another 22 PhD students and 3 Masters students.
\item I publish the \emph{Hyndsight} blog on research issues which receives an average of about 2000 pageviews per day.
\item I have produced 39 R packages as a result of my research; 27 of them are on CRAN.
\end{itemize}

\section{Research income}

I have acquired (in most cases jointly) about \$6.4 million in external research grants since 2000. I am currently a Chief Investigator for the Australian Centre of Excellence for Mathematical and Statistical Frontiers,  a Chief Investigator for two current ARC Linkage Grants, and I have research funding in 2019 from FaceBook Research and Advisian.

\section{Advisory boards}

%I am on several scientific advisory boards for external organizations:
\begin{compactitem}
\item
  Member of the Scaling committee, Victorian Tertiary Admissions Centre (1994--). %This committee is responsible for producing the ATAR for VCE students.
\item
  Member of the ATAR Technical Group for the Australasian Conference of Tertiary Admissions Centres (2003--).
\item
  Member of the Indigenous Statistical and Information Advisory Group for the Australian Institute of Health and Welfare (2017--).
\item
  Member of the Methodology Advisory Committee for the Australian Bureau of Statistics (2010--2018).
\end{compactitem}


\enlargethispage*{0.9cm}

\setlength{\bibitemsep}{1.8pt}

\printbib{books}
\printbib{selected}

\end{document}